Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-10 popl24/metalang.tex
checkpoint

When we consider the examples of GMW and YGC in detail below, our focus will be
on developing a codebase that can be used to define arbitrary
circuits, i.e., complete and concrete protocols. Since strings and
identifiers can be constructed manually, and expressions can occur
inside assignments and boolean expression forms, function definitions
can generalize over $\fedprot$-level patterns to obtain composable
program units. As a simple example, consider 3 party secret
sharing as illustrated in Example \ref{example-he}. We can
define a function $\ttt{share3}$ that abstracts the process
of splitting a given client's secret into 3 separate shares.
\begin{example} \label{example-share3} The function $\ttt{share3}$ 
  splits a client's secret into 3 shares returned as a record
  with fields $\ttt{s1-3}$:
  {\small
  \begin{verbatimtab}
      share3(client, secretid) {
        let s1 = flip[client, share1] in
        let s2 = flip[client, share2] in
        let s3 = (s1 xor s2) xor s[client, s: || secretid] in
        {s1 = s1;s2 = s2;s3 = s3}
      } \end{verbatimtab}
  }
  Here is a $\metaprot$ program that uses this function definition:
  {\small
    \begin{verbatimtab}
      let shares = share3(1, mysecret) in
      v[2,s1] := shares.s2;
      v[3,s1] := shares.s3 \end{verbatimtab}
  }
  which generates the following $\minifed$ program, as we formalize in Example \ref{example-share3-eval}
  below:
  {\small
  \begin{verbatimtab}
      v[2,s1] := flip[1, share2];
      v[3,s1] := flip[1, share1] xor flip[1, share2] xor s[1, s:mysecret] \end{verbatimtab}
  }
\end{example}

@@

{\footnotesize
\begin{verbatimtab}
  owl    :   string(gid)

  encode :   string(sa) * string(sb)

  andgg  :  string(g) * { k : bool[1]; p : bool[1] } *  { k : bool[1]; p : bool[1] }

  decode :  string(g) * { k : bool[1]; p : bool[1] }
\end{verbatimtab}
}

@@

In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality in Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates} includes the following:
\begin{itemize}
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol.
\item \ttt{encode}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
\begin{verbatimtab}
  andgate(0,s1,s2);
  garbledecode(0);
  let secrets = encode(s1,s2) in
  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
\end{verbatimtab}
\end{example}

>>>>

When we consider the examples of GMW and YGC in detail below, our
focus will be on developing a codebase that can be used to define
arbitrary circuits, i.e., complete and concrete protocols. Since
strings and identifiers can be constructed manually, and expressions
can occur inside assignments and boolean expression forms, function
definitions can generalize over $\fedprot$-level patterns to obtain
composable program units. \cnote{Cur the following example to save
  space?.}  As a simple example, consider 3 party secret sharing as
illustrated in Example \ref{example-he}. We can define a function
$\ttt{share3}$ that abstracts the process of splitting a given
client's secret into 3 separate shares.
\begin{example} \label{example-share3} The function $\ttt{share3}$ 
  splits a client's secret into 3 shares returned as a record
  with fields $\ttt{s1-3}$:
  {\small
  \begin{verbatimtab}
      share3(client, secretid) {
        let s1 = flip[client, share1] in
        let s2 = flip[client, share2] in
        let s3 = (s1 xor s2) xor s[client, s: || secretid] in
        {s1 = s1;s2 = s2;s3 = s3}
      } \end{verbatimtab}
  }
  Here is a $\metaprot$ program that uses this function definition:
  {\small
    \begin{verbatimtab}
      let shares = share3(1, mysecret) in
      v[2,s1] := shares.s2;
      v[3,s1] := shares.s3 \end{verbatimtab}
  }
  which generates the following $\minifed$ program, as we formalize in Example \ref{example-share3-eval}
  below:
  {\small
  \begin{verbatimtab}
      v[2,s1] := flip[1, share2];
      v[3,s1] := flip[1, share1] xor flip[1, share2] xor s[1, s:mysecret] \end{verbatimtab}
  }
\end{example}

@@

@@

In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality in Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates} includes the following:
\begin{itemize}
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol.
\item \ttt{encode}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\footnotesize
\begin{verbatimtab}
  let secrets = encode("s1","s2") in v[0,output] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}
